From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-04 Pi+/paper/equivalence.tex
Revise UFin section and fit into page budget

In principle, the normalized program can be produced following two strategies: (i) by repeatedly applying the rewrite
rules of our calculus of reversible functions (explained in Sec.~\ref{sec:reversibletwo}), or (ii) in the case above by
using a normalization-by-evaluation (NBE) process that evaluates the program to a permutation on a finite set of 8
elements and reifies that permutation back to a program. The key idea of the NBE process is a systematic way to express
permutations as sequences of adjacent swaps as illustrated in the following small example where the permutation on the
left is compiled to the sequence of four adjacent transpositions on the right:

@@

\paragraph*{Program synthesis.} The NBE process embodies a quoting mechanism that synthesizes programs from
permutations. Indeed, instead of writing a program for \Afun{reset 2}, one might simply specify the desired permutation as:

>>>>

In principle, the normalized program can be produced following two strategies: (i) by repeatedly applying the rewrite
rules of our calculus of reversible functions (explained in Sec.~\ref{sec:reversibletwo}), or (ii) in the case above by
using a normalization-by-evaluation (NbE) process that evaluates the program to a permutation on a finite set of 8
elements and reifies that permutation back to a program. The key idea of the NbE process is a systematic way to express
permutations as sequences of adjacent swaps as illustrated in the following small example where the permutation on the
left is compiled to the sequence of four adjacent transpositions on the right:

@@

\paragraph*{Program synthesis.} The NbE process embodies a quoting mechanism that synthesizes programs from
permutations. Indeed, instead of writing a program for \Afun{reset 2}, one might simply specify the desired permutation as:

### 2021-07-04 Pi+/paper/finite.tex
Add some text in section 6
Revise UFin section and fit into page budget

@@

By composing~\cref{prop:lehmer-aut-equiv} and~\cref{prop:sn-im-lehmer-equiv}, we obtain the final equivalence.

>>>>

We would like to give a syntactic presentation for this groupoid. Note that, in $\BFin$, the set of bijections on a
finite set of cardinality $n$ has a group structure -- the identity function is the neutral element, group
multiplication is given by function composition, and the group inverse is given by inverting the bijection. This is the
automorphism group of the finite set, which is also known to be the finite symmetric group $\Sn[n]$.

Groups can be defined by listing the carrier set and the operations of the group, or they can be described using a group
presentation, which gives the generators and relations of a group. The last step of our technical development is to use
a group presentation for $\Sn$ to give a presentation for the higher cells of the groupoid $\UFin$. Using this
characterisation, we will obtain our completeness result.

@@

By composing~\cref{prop:lehmer-aut-equiv} and~\cref{prop:sn-lehmer-fin-equiv}, we obtain the final equivalence.
